Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-08 ccppabc/text/revision/main.tex
More edits to Section 3.4. This time directed towards Ref Report Comment 2 (issue #15)

Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} 
($\xigg$ and $\gmf$). 
{\bf \color{darkgreen}
CHH: Need a sentence here that reiterates that the Gaussian functional form 
assumption is incorrect and especially incorrect for the GMF observable case.
Also, for us to say the following sentence, we need to talk about it more explicitly 
when discussing Figures 7,8,9, and 10. 
}

@@

\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_contour_nbargmf.pdf}
\caption{\label{fig:cont_nbargmf} 
{\bf \color{dred}
Same as Figure \ref{fig:cont_nbarxi}, but using $\ngalaxy$ and $\gmf(N)$ as 
observables. Again, the confidence regions derived from both methods are 
consistent with the ``true'' HOD parameters used to generate the mock 
observations. The confidence region of $\alpha$ from the Gaussian 
pseudo-likelood method is biased compared to the ABC-PMC contours. 
This may be due to the fact that the true likelihood function that 
describes $\gmf(N)$ deviates significantly from the assumed Gaussian 
functional form.}
%\end{center}
\end{figure*}

>>>>

{\bf \color{dred}
Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} (\emph{e.g.} $\xigg$ and $\gmf$). 
}
{\bf \color{darkgreen}
CHH: Need a sentence here that reiterates that the Gaussian functional form 
assumption is incorrect and especially incorrect for the GMF observable case.
}
{\bf \color{dred}
In the case where the observable $\gmf(N)$ is used as a summary statistic
of a galaxy catalog, assuming a Gaussian functional form for the likelihood
would clearly misreprenset the true likelihood function. In fact, this 
discrepancy may explain the less biased constraints from the ABC-PMC analysis 
compared to the Gaussian-likelihood analysis in \ref{fig:cont_nbargmf}.
}

@@

\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_contour_nbargmf.pdf}
\caption{\label{fig:cont_nbargmf} 
{\bf \color{dred}
Same as Figure \ref{fig:cont_nbarxi}, but using $\ngalaxy$ and $\gmf(N)$ as 
observables. Again, the confidence regions derived from both methods are 
consistent with the ``true'' HOD parameters used to generate the mock 
observations. The confidence region of $\alpha$ from the Gaussian 
pseudo-likelood method is biased compared to the ABC-PMC contours. 
This may be due to the fact that the true likelihood function that 
describes $\gmf(N)$ deviates significantly from the assumed Gaussian 
functional form.}
}
%\end{center}
\end{figure*}
